j_play

### 2020-11-30 scripts/draft_play.Rmd
Urban/Rural exploration chunks

>>>>

```{r rural play}
#Data Prep
rural_districts <- district_class %>% 
  janitor::clean_names() %>% 
  filter(district_classification == "Rural") %>% 
  select(-c("data_level",
            "public_or_independent",
            "district_population_2016"))

#Viz - Totals by Code
ggplot(rural_districts, 
       aes(special_needs_code, number_of_students,
           color = special_needs_code)) +
  geom_line() +
  facet_wrap(~school_year) +
  labs(title = "Total Students by Exceptionality",
       x = "Exceptionality",
       y = "Number of Students")

#Data for Rural Totals (No categories)
rural_totals <- rural_districts %>% 
  group_by(school_year, district_name, district_number) %>% 
  mutate(students = sum(number_of_students, na.rm = TRUE)) %>% 
  select(-c(special_needs_code, district_classification, number_of_students)) %>% 
  distinct()

#Data Viz Totals/Time
ggplot(rural_totals, aes(school_year, students)) +
  geom_col(aes(color = district_name)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

#What's going on with Prince George? Why is there such a steep drop in 2006?
pg <- rural_districts %>% 
  filter(district_name == "Prince George") %>% 
  as_tibble()

pg_sums <- pg %>% 
  group_by(school_year) %>% 
  mutate(student = sum(number_of_students, na.rm = TRUE)) %>% 
  select(-c(district_number, special_needs_code, district_classification, number_of_students)) %>% 
  distinct()

#What's happening by Dx?
pg_dx_sum <- pg %>% 
  group_by(school_year, special_needs_code) %>% 
  mutate(student = sum(number_of_students, na.rm = TRUE)) %>% 
  select(-c(district_number, district_classification, number_of_students)) %>% 
  distinct()

ggplot(pg_dx_sum, aes(school_year, student)) +
  geom_col() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_wrap(~special_needs_code)

#What's going on with gifted?????
pg_gifted <- pg %>% 
  filter(special_needs_code == "P") %>% 
  select(-c(district_number, district_classification))

ggplot(pg_gifted, aes(school_year, number_of_students)) +
  geom_col() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r urban play}
#Data Prep
urban_districts <- district_class %>% 
  janitor::clean_names() %>% 
  filter(district_classification == "Urban") %>% 
  select(-c("data_level",
            "public_or_independent",
            "district_population_2016"))

urban_totals <- urban_districts %>% 
  group_by(school_year, district_name, district_number) %>% 
  mutate(students = sum(number_of_students, na.rm = TRUE)) %>% 
  select(-c(special_needs_code, district_classification, number_of_students)) %>% 
  distinct()

#Data Viz Totals/Time
ggplot(urban_totals, aes(school_year, students)) +
  geom_col(aes(color = district_name)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

#Viz - Totals by Code
ggplot(urban_districts, 
       aes(special_needs_code, number_of_students,
           color = special_needs_code)) +
  geom_line() +
  facet_wrap(~school_year) +
  labs(title = "Total Students by Exceptionality",
       x = "Exceptionality",
       y = "Number of Students")
```

### 2020-11-30 scripts/j_play.Rmd
Urban/Rural exploration chunks

@@

>>>>

count_by_year <- BCdata %>% 
  janitor::clean_names() %>% 
  group_by(school_year, special_needs_desc) %>% 
  mutate(total_students = sum(number_of_students, na.rm = TRUE)) %>% 
  select("school_year",
         "special_needs_desc",
         "total_students") %>% 
  pivot_wider(names_from = school_year,
              values_from = total_students) %>% 
  drop_na()

@@

```{r rural play}
#Data Prep
rural_districts <- district_class %>% 
  janitor::clean_names() %>% 
  filter(district_classification == "Rural") %>% 
  select(-c("data_level",
            "public_or_independent",
            "district_population_2016"))

#Viz - Totals by Code
ggplot(rural_districts, 
       aes(special_needs_code, number_of_students,
           color = special_needs_code)) +
  geom_line() +
  facet_wrap(~school_year) +
  labs(title = "Total Students by Exceptionality",
       x = "Exceptionality",
       y = "Number of Students") +
  scale_color_manual(name = "Special Needs Description",
                    labels = c("A - Physically Dependent",
                               "B - Deafblind",
                               "C - Moderate to Profound Intellectual Disability",
                               "D - Physical Disability or Chronic Health Impairment",
                               "E - Visual Impairment",
                               "F - Deaf or Hard of Hearing",
                               "G - Autism Spectrum Disorder",
                               "H - Inten Behav Inter/Serious Mental Illness",
                               "J - Severe Learning Disabilities",
                               "K - Mild Intellectual Disability",
                               "M - Behavior Disorder (Moderate)",
                               "N - Behavior Disorder (Rehabilitation)",
                               "P - Gifted",
                               "Q - Learning Disability",
                               "R - Moderate Behaviour Support/Mental Illness"))

rlang::last_error()
```

```{r codes and descs}
code_key <- bc_data_district_classification %>% 
  janitor::clean_names() %>% 
  select(special_needs_code, special_needs_desc) %>% 
  distinct()
```
